Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink: sota

@@

Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates. 
Each agent then learns a deterministic policy based on its local observations. % 
Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 

@@

Another class of algorithms, called \emph{value-based} methods, learn a value function that estimates the expected return for each agent.

@@

VDN factorizes the joint Q-function into a sum of individual agent Q-functions, 
simplifying the learning process. 
QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
allowing for more complex representations of joint action values. % 

@@

the one that models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent.

@@

In this context, mean field q-learning (Mean-Q)~\cite{DBLP:conf/icml/YangLLZZW18} has been proposed.
This approach scales well to large numbers of agents and has been successful in various applications. 

@@

There are also modern solution which leverages collective abstraction to reduce the complexity of the problem, such as the one proposed in field-informed reinforcement learning~\cite{DBLP:conf/acsos/AguzziVE23}.

>>>>

In this family, the most popular algorithms are MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{yu2022surprising}.

@@

%Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates. 
%Each agent then learns a deterministic policy based on its local observations. % 
%Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
%MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 

@@

Another class of algorithms, called \emph{value-based} methods, learn a value function that estimates the expected return from a global point of view while maintaining decentralized policies.

@@

%VDN factorizes the joint Q-function into a sum of individual agent Q-functions, 
%simplifying the learning process. 
%QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
%allowing for more complex representations of joint action values. % 

@@

it models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent~\cite{DBLP:conf/icml/YangLLZZW18}.

@@

%In this context, mean field q-learning (Mean-Q)~\cite{DBLP:conf/icml/YangLLZZW18} has been proposed.
%This approach scales well to large numbers of agents and has been successful in various applications. 

@@

There are also novel solutions which leverage collective abstraction to reduce the complexity of the problem, such as field-informed reinforcement learning~\cite{DBLP:conf/acsos/AguzziVE23}.
